### 2022-05-26 main/chapter_2ljets.tex
fill in more on jets

Baseline leptons are required only to have  $\pt > 3~\eV[G]$ for muons and
$\pt > 4.5~\eV[G]$ for electrons.
Signal leptons are all required to have $\pt > 10~\eV[G]$, along with tighter
quality and isolation requirements, details of which can be found in the
paper~\cite{atlas2022searches}.

@@

Like leptons, jets are identified with `baseline' and `signal' requirements
with increasingly tight requirements on quality metrics and kinematics.

\TODO{anti-kt 0.4}

Baseline jets require $\pt > 20~\eV[G]$, and signal jets require
$\pt > 30~\eV[G]$.
The $\twoljets$ electroweak analysis uses only signal jets unless those jets
are $b$-tagged.

>>>>

Baseline leptons are required only to have  $\pt > 3~\eV[G]$ for muons and
$\pt > 4.5~\eV[G]$ for electrons.
Signal leptons are all required to have $\pt > 10~\eV[G]$, along with tighter
quality and isolation requirements, details of which are given in the
paper~\cite{atlas2022searches}.
Electrons are accepted within $|\eta| < 2.47$.
Baseline muons have $|\eta| < 2.7$, and signal muons have $|\eta| < 2.6$.

@@

Like leptons, hadronic jets are identified with `baseline' and `signal'
requirements with increasingly tight requirements on quality metrics and
kinematics.

Jets in $\twoljets$ use the anti-$k_t$ algorithm with the standard small radius
parameter of $R=0.4$~\cite{jet_anti_kt}.
Jets are formed from ``topological'' clusters of energy deposits in the
calorimeters~\cite{atlas_jet_topo_PERF_2014_07}.

This topological clustering algorithm is not the latest \atlas\ jet algorithm;
it has been supplanted in recent years by a `particle flow' method, which
uses tracking information to improve the reconstruction of charged
hadrons~\cite{atlas_jet_pflow_PERF_2015_09}.
We did not switch to these improved jets because the change would have required
further delays.

Baseline jets are defined require $\pt > 20~\eV[G]$, and signal jets require
$\pt > 30~\eV[G]$.
Again, details of quality criteria and angular selections
The $\twoljets$ electroweak analysis uses only signal jets unless those jets
are $b$-tagged.
